### 2021-07-14 chapters/1_abstract.tex
acr fuzzy c-means

\documentclass[../main]{subfiles}
\begin{document}
\chapter*{Abstract}
Software testing is a crucial part of the software engineering process. 
It is widely used in the industry.
A part of software testing is building test suites which contain unit tests.
These unit tests are written by developers. 
As projects grow the test suite grows along.
Maintaining and monitoring these test suites is important because they influence the cost of maintenance.
Monitoring the quality of test code has shown that tests with lower quality leads to more defect-prone production code.
\newline
Measuring the effectiveness of test suites detecting faults is part of the monitoring process.
A technique to measure the test effectiveness is mutation testing.
Mutation testing is a computationally expensive technique that requires the ability to run tests.
Different techniques have been proposed to reduce the cost of mutation testing.
One of these techniques is the clustering of mutants.
By clustering mutants we can execute less mutants to reduce the cost.
\newline
We conducted two experiment in which we cluster the mutants with two different techniques.
Before conducting the experiment we conducted a state of the art comparison between three mutation testing tools for Java.
Based on this research we selected a mutation testing tool to use in our experiments.
\newline
We started our experiment by identifying characteristics to represent the mutants.
For the first experiment we used hierarchical clustering and in the second experiment we trained the fuzzy c-means model.
We calculated a weighted mutation score and compared this with the mutation score of a full set of mutants executed.
Results show that with hierarchical clustering we can reduce the amount of mutants executed while maintaining the effectiveness.
The clusters generated by the machine learning model were less accurate and showed a significant decrease in effectiveness.
The machine learning model didn't perform as well as the hierarchical clustering.
However, more work is needed in finding the right parameters for the fuzzy c-means algorithm. 
\end{document}

>>>>

\documentclass[../main]{subfiles}
\begin{document}
\chapter*{Abstract}
Software testing is a crucial part of the software engineering process. 
It is widely used in the industry.
A part of software testing is building test suites which contain unit tests.
These unit tests are written by developers. 
As projects grow the test suite grows along.
Maintaining and monitoring these test suites is important because they influence the cost of maintenance.
Monitoring the quality of test code has shown that tests with lower quality leads to more defect-prone production code.
\newline
Measuring the effectiveness of test suites detecting faults is part of the monitoring process.
A technique to measure the test effectiveness is mutation testing.
Mutation testing is a computationally expensive technique that requires the ability to run tests.
Different techniques have been proposed to reduce the cost of mutation testing.
One of these techniques is the clustering of mutants.
By clustering mutants we can execute less mutants to reduce the cost.
\newline
We conducted two experiment in which we cluster the mutants with two different techniques.
Before conducting the experiment we conducted a state of the art comparison between three mutation testing tools for Java.
Based on this research we selected a mutation testing tool to use in our experiments.
\newline
We started our experiment by identifying characteristics to represent the mutants.
For the first experiment we used hierarchical clustering and in the second experiment we trained the \acrlong{fcm} model.
We calculated a weighted mutation score and compared this with the mutation score of a full set of mutants executed.
Results show that with hierarchical clustering we can reduce the amount of mutants executed while maintaining the effectiveness.
The clusters generated by the machine learning model were less accurate and showed a significant decrease in effectiveness.
The machine learning model didn't perform as well as the hierarchical clustering.
However, more work is needed in finding the right parameters for the \acrlong{fcm} algorithm. 
\end{document}

### 2021-07-14 chapters/rq2/1_experiment_design.tex
acr fuzzy c-means

\subsubsection{Self organizing map, C-means and fuzzy C-means}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and fuzzy C-means models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled in the experiment.
They observe that the C-means and fuzzy C-means had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for Fuzzy C-means which was very stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was very affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being very affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also conclude that their results partially overlap with other research in the same domain.
\newline
Based on these results we can conclude that the fuzzy c-means model has the best performance overall.
For this experiment we select the fuzzy c-means model.

@@

\subsection{Implementation of algorithm}
The research paper of the fuzzy c-means algorithm is referenced in the survey paper of Du et al\cite{Du2010Clustering:Approach}.
The fuzzy c-means algorithm is developed by Bezdek et al.\cite{Bezdek1984FCM:Algorithm}.
Based on their research an implementation can be developed.
There are existing libraries that contain the implementation of the fuzzy c-means algorithm.
Developing our own version of the fuzzy c-means algorithm is out of scope for this research.
For this reason we choose to use a library that implements the fuzzy c-means algorithm.
The library we will use for this experiment is the fuzzy c-means implementation build by Dias et al.\cite{dias2019fuzzy}.
The theory developed by Bezdek et al., is implemented in this library.
The library has been used in other research\cite{DeAlmeidaNeto2020, Kopf2019, Nwadiugwu2020} and is actively maintained.

\subsection{Algorithm parameters}
The fuzzy c-means algorithm has to initialize the centroids of the clusters.
Our selected library does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible and deterministic we will use a generated seed.
The seed generated is included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the fuzzy c-means model\cite{Bezdek1995OnModel}.
They researched what effect which parameters have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is probably in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the fuzzy c-means more robust to noise and outliers.
He suggests implementing fuzzy c-means with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier\textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise and outliers we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are some techniques available to estimate the number of clusters.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the number of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the number of clusters.
We can use this number for the number of clusters parameter in the fuzzy c-means algorithm.

>>>>

\subsubsection{Self organizing map, C-means and \acrlong{fcm}}
\label{ch:topThreeModels}
The \acrfull{som}, C-means and \acrfull{fcm} models are all models that would fit our purpose. 
To choose between these models we will look at the performance of each model.
Mingoti et al., compared the performance of these three models \cite{Mingoti2006ComparingAlgorithms}.
They did a Monte Carlo simulation where the cluster sizes and amount of random numbers in the data set varied each simulation\cite{Mingoti2006ComparingAlgorithms}.
Other variables such as cluster boundaries and overlap were also controlled in the experiment.
They observe that the C-means and \acrlong{fcm} had good performance for non overlapping situations\cite{Mingoti2006ComparingAlgorithms}.
The best results for average recovery and internal dispersion rates were found for \acrlong{fcm} which was very stable in all situations achieving recovery averages over 90\%\cite{Mingoti2006ComparingAlgorithms}
The C-means method was very affected by the presence of a large amount of outliers.
They conclude that the \acrshort{som} did not perform well in many cases being very affected by the amount of variables and clusters even for the non overlapping cases\cite{Mingoti2006ComparingAlgorithms}.
They also conclude that their results partially overlap with other research in the same domain.
\newline
Based on these results we can conclude that the \acrshort{fcm} model has the best performance overall.
For this experiment we select the \acrshort{fcm} model.

@@

\subsection{Implementation of algorithm}
The research paper of the \acrshort{fcm} algorithm is referenced in the survey paper of Du et al\cite{Du2010Clustering:Approach}.
The \acrshort{fcm} algorithm is developed by Bezdek et al.\cite{Bezdek1984FCM:Algorithm}.
Based on their research an implementation can be developed.
There are existing libraries that contain the implementation of the \acrshort{fcm} algorithm.
Developing our own version of the \acrshort{fcm} algorithm is out of scope for this research.
For this reason we choose to use a library that implements the \acrshort{fcm} algorithm.
The library we will use for this experiment is the \acrlong{fcm} implementation build by Dias et al.\cite{dias2019fuzzy}.
The theory developed by Bezdek et al., is implemented in this library.
The library has been used in other research\cite{DeAlmeidaNeto2020, Kopf2019, Nwadiugwu2020} and is actively maintained.

\subsection{Algorithm parameters}
The \acrshort{fcm} algorithm has to initialize the centroids of the clusters.
Our selected library does this based on a random number.
It also allows us to control this random number.
To make the initialization of the centroid reproducible and deterministic we will use a generated seed.
The seed generated is included in the Github repository\cite{rbasarat-repo}.
\newline
Bezdek et al., also researched cluster validity for the \acrshort{fcm} model\cite{Bezdek1995OnModel}.
They researched what effect which parameters have on the validity of the clusters.
They specifically analyzed the role of weighting exponent \textit{m}(fuzziness parameter).
They concluded that the best choice for \textit{m} is probably in the interval [1.5, 2.5], whose mean and midpoint is \textit{m}=2.
Wu proposed a new guideline for selecting parameter \textit{m}\cite{Wu2012}.
His point of view was that a large \textit{m} value will make the \acrlong{fcm} more robust to noise and outliers.
He suggests implementing \acrlong{fcm} with \textit{m}=[1.5, 4].
When the data set contains noise and outliers, the fuzzifier\textit{m}=4 is recommended in a theoretical upper bound case.
Since our data set does not contain noise and outliers we choose to select the midpoint concluded in the research of Bezdek et al.\cite{Bezdek1995OnModel}.
The value of \textit{m} in this experiment is 2.
\newline
Finding the correct amount of clusters has been an ongoing problem for clustering algorithms\cite{Du2010Clustering:Approach}.
Fortunately there are some techniques available to estimate the number of clusters.
During model selection we discussed the mountain and subtractive models. 
These models are designed to estimate the number of clusters in a data set.
The subtractive clustering model is specifically designed to approximate the number of clusters for fuzzy system models\cite{Chiu1994FuzzyEstimation}.
It approximates the centroids and amount of the clusters based on the data points in the data set\cite{Chiu1994FuzzyEstimation}.
We will select and implement the subtractive clustering model to estimate the number of clusters.
We can use this number for the number of clusters parameter in the \acrshort{fcm} algorithm.
